### 2023-04-23 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

This chapter is about describing the metodology and developments to achieve the project goals.

>>>>

This chapter is about describing the methodology and developments to achieve the project goals. 
Firstly, let me begin by elaborating on the workings of the classification process in the processing thread. Moving on, I will then delve into the operational sequences of the controller thread. Lastly, I will provide an explanation on the implementation of the controller.

### 2023-04-23 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@

>>>>

The results of the classification process were favorable for experiment automation, however, they may not be as effective for optimal performance of the controller.
The inaccuracy of the classification by statistical method in addition with the amount of variables that need to be syntonized for stabilize in cone jet or multi jet makes difficult the controller development.

@@

    Of particular interest in applications is the cone-jet mode, where the meniscus emits a steady microscopic jet, resulting in uniformly sized droplets.
